Simply Grasping Simple Shapes:\\ Commanding a Humanoid Hand with a Shape-Based Synergy

### 2017-10-11 draft_springer_2.tex
updated abstract, reorganized results and discussion

\begin{abstract}
Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects. There exists a need for an efficient method to command high degree-of-freedom (DoF) dexterous manipulators for a range of objects such that explicit models are not needed for every interaction. The authors propose a method incorporating the neuroscience concept of synergies to decrease the commanded DoFs to match intuitive measurements of an object, which we term geometrical synergies. Using the SynGrasp toolbox, a model of Robonaut 2`s twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter. Experiments were performed on the robot to validate and update the synergy-based models.  Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated experimentally. This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects the robot can manipulate.
\keywords{Manipulation, grasp, synergy, humanoid, dexterous, hand}
\end{abstract}

@@

In practice, many humanoid systems will use some model based approach to manipulate objects encountered in the world. This can be seen through the DARPA Robotics Competition (DRC) Trials in the ways the teams commanded their humanoids to interact with things like drills, door handles, valves, and other objects. \cite{DRC_Yanco}, \cite{IHMC}. Currently, the R2 project is using the Affordance Templates (AT) framework, initially presented in \cite{affordance_templates}. This system allows a model of an object to be created with different end effector waypoints to create allowable affordances for manipulating the object. Through this AT model, a catalog of different objects with their affordances is created and stored to be used throughout the manipulation process. However, in the current implementation, each new object encountered must have a new Affordance Template created before it can be manipulated. If generic models were available, any new object encountered that fit closely enough to an existing model could be used immediately, with no further development time.

@@

\subsection{Testing Method} 
A simple testing method was used to validate the models, as well as perform the final experiments to determine grasp efficacy. A cylindrical object was placed on the table, touching R2's open palm. The object's placement along the palm was varied from near the base of the fingers to the base of the thumb. This allowed testing of uncertainty in position that will be present when the object must be localized. Then, the robot was commanded to close its hand based on the synergy values, lift the object, rotate the object upside down, return it to straight, and finally, release it back on the table. This set of motions demonstrates a firm grasp on the object through a large motion of the robot.

>>>>

\begin{abstract}
Despite rapid advancements in dexterity and mechanical design, the utility of humanoid robots in an uncontrolled laboratory setting is limited in part due to the complexity involved in programming robots to grasp common objects. There exists a need for an efficient method to command high degree-of-freedom (DoF) dexterous manipulators for a range of objects such that explicit models are not needed for every interaction. The authors propose a method incorporating the neuroscience concept of postural synergies to decrease the commanded DoFs to match intuitive measurements of an object, which we term geometrical synergies.  The approach of this paper is similar to that of Ciocarlie et al. \cite{ciocarlieallen}, however, rather than testing the postural synergies that come from the principle components of a human grasps, the authors design a grasping synergy based on the object that is meant to be grasped.  For this paper, the synergy was designed to grasp cylinder-shaped objects. Using the SynGrasp toolbox, a model of Robonaut 2`s twelve-DoF hand was created to perform contact analysis around a small set of cylinders defined by a single variable, diameter. Experiments were performed on the robot to validate and update the synergy-based models.  Successful manipulation of a large range of cylindrical objects, not previously introduced to the robot, was demonstrated in a proof-of-concept experiment. This synergy-based grasp planning method can be applied to any humanoid hand to decrease the number of commanded DoF based on simple, measureable inputs, to grasp commonly shaped objects, vastly multiplying the library of objects the robot can manipulate.
\keywords{Manipulation, grasp, synergy, humanoid, dexterous, hand}
\end{abstract}

@@

In practice, many humanoid systems will use some model based approach to manipulate objects encountered in the world. This can be seen through the DARPA Robotics Challenge (DRC) Trials in the ways the teams commanded their humanoids to interact with things like drills, door handles, valves, and other objects. \cite{DRC_Yanco}, \cite{IHMC}. Currently, the R2 project is using the Affordance Templates (AT) framework, initially presented in \cite{affordance_templates}. This system allows a model of an object to be created with different end effector waypoints to create allowable affordances for manipulating the object. Through this AT model, a catalog of different objects with their affordances is created and stored to be used throughout the manipulation process. However, in the current implementation, each new object encountered must have a new Affordance Template created before it can be manipulated. If generic models were available, any new object encountered that fit closely enough to an existing model could be used immediately, with no further development time.

@@

\subsection{Testing Method} 
A simple testing method was used to validate the models, as well as perform the final experiments to determine grasp efficacy. A cylindrical object was placed on the table, touching R2's open palm. All fingers were fully extended in the starting position.  The object's placement along the palm was varied from near the base of the fingers to the base of the thumb. This allowed testing of uncertainty in position that will be present when the object must be localized. Then, the robot was commanded to close its hand based on the synergy values, lift the object, rotate the object upside down, return it to straight, and finally, release it back on the table. This set of motions demonstrates a firm grasp on the object through a large motion of the robot.
